### 2024-03-27 course/statml/2024/project/project.tex
final project

\subitem(b) \emph{ONE short presentation video within 10 mins}, e.g. in Youtube or Bilibili link. You may submit your presentation slides together with the video link to help understanding.

@@

\subsection{Type-II diabetes and Alzheimer's disease}

This project is about the study on type-II diabetes and Alzheimer's Disease. It is confirmed that Type-II diabetes patient has higher risk of getting Alzheimer's disease
Research revealed that the brain connectivity strength changed in Type-II diabetes patients even before they showed impairment in cognition. MRI can collect the brain connectivity strength between each pair of brain regions. Therefore, it may enable us to explore the following scientific questions. Can we use brain connectivity features to distinguish type-II diabetes and healthy people in control group? Can we use brain connectivity features to predict clinical symptoms of type-II diabetes? With so many connectivity features, which are the top 5/10 features that contributed most to the classification and symptom prediction of type-II diabetes?

We will explore this question based on a dataset collected by No.1 Affiliated Hospital of GUCM which co-worked with WEI Yue. We have one under reviewing paper on this dataset, not published yet. For detailed description about this project, please refer to the following slides:

\noindent \url{https://yao-lab.github.io/course/statml/2022/slides/MATH\_5470\_probject\_intro\_MAR2022.pdf}

>>>>

\subitem*(b)\footnote{We plan to do final project presentation in the last lecture.} \emph{ONE short presentation video within 10 mins}, e.g. in Youtube or Bilibili link. You may submit your presentation slides together with the vieo link to help understanding.

@@

%\subsection{Type-II diabetes and Alzheimer's disease}
%
%This project is about the study on type-II diabetes and Alzheimer's Disease. It is confirmed that Type-II diabetes patient has higher risk of getting Alzheimer's disease
%Research revealed that the brain connectivity strength changed in Type-II diabetes patients even before they showed impairment in cognition. MRI can collect the brain connectivity strength between each pair of brain regions. Therefore, it may enable us to explore the following scientific questions. Can we use brain connectivity features to distinguish type-II diabetes and healthy people in control group? Can we use brain connectivity features to predict clinical symptoms of type-II diabetes? With so many connectivity features, which are the top 5/10 features that contributed most to the classification and symptom prediction of type-II diabetes?
%
%We will explore this question based on a dataset collected by No.1 Affiliated Hospital of GUCM which co-worked with WEI Yue. We have one under reviewing paper on this dataset, not published yet. For detailed description about this project, please refer to the following slides:
%
%\noindent \url{https://yao-lab.github.io/course/statml/2022/slides/MATH\_5470\_probject\_intro\_MAR2022.pdf}
